---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tabulate


<!-- badges: start -->

[![R build status](https://github.com/markitr/tabulate/workflows/R-CMD-check/badge.svg)](https://github.com/markitr/tabulate/actions?workflow=R-CMD-check)
[![Codecov test coverage](https://codecov.io/gh/markitr/tabulate/branch/main/graph/badge.svg)](https://codecov.io/gh/markitr/tabulate?branch=main)
[![R-CMD-check](https://github.com/markitr/tabulate/workflows/R-CMD-check/badge.svg)](https://github.com/markitr/tabulate/actions)


<!-- badges: end -->

## Overview

The goal of tabulate is to help you create tabular data in long format from a dataframe where: 

1. The output is predictable every time.
2. You can group and cross any variable. 
3. You can use regex to match on almost any argument.


## Installation

### Development version

To get a bug fix or to use a feature from the development version, you can install the development version of dplyr from GitHub.

```{r, eval = FALSE}
# Or the development version from GitHub:
# install.packages("devtools")
devtools::install_github("markitr/tabulate")
```


---

Please note that the tidyr project is released with a [Contributor Code of Conduct](docs/code_of_conduct.md). By contributing to this project, you agree to abide by its terms.
